There once was a grid at ol' Carkeek

### 2016-05-04 Manuscript/v0.0/carkeek_grid.tex
incorporate Ole figures

Samples collected of ecological communities may vary in dissimilarity from 0 (completely identical) to 1 (completely different). 
For samples collected from multiple locations, the relationship between their spatial distance and community dissimilarity is of interest because it reflects the amount of community heterogeneity over the spatial scale sampled.
%In general, the relationship between community dissimilarity (0 = identical; 1 = completely different) and spatial distance is expected to be asymptotic, because communities nearer to each other tend to be more similar than those farther apart.
The intercept is expected to be 0, because only within-sample comparisons can have 0 spatial separation, and communities have no dissimilarity within a sample. % technically impossible for samples to be taken at exactly 0; they are actually immediately adjacent.
Likewise, dissimilarity cannot exceed 1. 
Deviation from 0 indicates heterogeneous community composition/structure over fine scales.
A flat relationship between dissimilarity and distance indicates that heterogeneity is not assorted spatially, and can be interpreted in different ways, depending on the mean.
If the mean is close to 1, there is high spatial heterogeneity over the spatial scale of sampling.
If the mean is 0, all samples are identical, and we infer there is complete community homogeneity over the scale sampled.
The rate at which community dissimilarity approaches the mean gives an indication of the rate of community turnover.

@@

\subsection*{Laboratory Methods}
We collated coarse-scale data on life history characteristic for each of the major taxonomic groups recovered, 
including dispersal range of the gametes, larvae, and adults, adult habitat type and selectivity, and adult body size. 
Dispersal range was given as an order-of-magnitude approximation of the scale of dispersal: for example, internally fertilized species were assigned a gamete range of 0 km, while broadcast spawners were assigned a gamete range of 10 km. 
Similarly, adult range size was approximated as 0 km (sessile), 1 km (motile but not pelagic), or 10 km (highly mobile, pelagic). 
Variables were specified as 'multiple' for groups known to span more than 1 magnitude of range size. 
For groups to which sequences were annotated with high confidence, but for which life history strategy is diverse or poorly known (e.g. families in the phylum Nemertea), we used conservative, coarse approximations at a higher taxonomic rank. 
We assessed whether or not marine invertebrate taxa are thought to be present in Puget Sound by checking for their presence in a comprehensive checklist of invertebrates of Puget Sound CITE KOZLOFF. 
These data are available as part of the REFERENCE SUPPLEMENTAL DATA.

@@

>>>>

Samples collected of ecological communities may vary in dissimilarity from 0 (completely identical) to 1 (completely different). 
For samples collected from multiple locations, the relationship between their spatial distance and community dissimilarity is of interest because it reflects the amount of community heterogeneity---changes in abundance and composition---over the spatial scale sampled. 
%In general, the relationship between community dissimilarity (0 = identical; 1 = completely different) and spatial distance is expected to be asymptotic, because communities nearer to each other tend to be more similar than those farther apart.
The intercept is expected to be 0, because only within-sample comparisons can have 0 spatial separation, and communities have no dissimilarity within a sample if sampling method is repeatable. % technically impossible for samples to be taken at exactly 0; they are actually immediately adjacent.
%Deviation from 0 indicates heterogeneous community composition/structure over fine scales. 
Likewise, dissimilarity cannot exceed 1, and reaches 1 only when multiple discrete community types are sampled.
The trend is expected to be asymptotic if communities within a habitat are spatially structured, where the value of the asymptote and the rate of increase provide insight about community turnover. 
A flat relationship indicates that heterogeneity is not assorted spatially, and can be interpreted in different ways, depending on the asymptote. % ?or no relationship both 
If the asymptote is close to 1, there is high spatial heterogeneity over the spatial scale of sampling. 
If the asymptote is close 0, all samples are similar, and we infer there is complete community homogeneity over the scale sampled. 
The rate at which community dissimilarity approaches the mean gives an indication of the rate of community turnover.

@@

\subsection*{Organismal Life History Data}
We collated coarse-scale data on life history characteristic for each of the major taxonomic groups recovered, 
including dispersal range of the gametes, larvae, and adults, adult habitat type and selectivity, and adult body size. 
Dispersal range was given as an order-of-magnitude approximation of the scale of dispersal: for example, internally fertilized species were assigned a gamete range of 0 km, while broadcast spawners were assigned a gamete range of 10 km. 
Similarly, adult range size was approximated as 0 km (sessile), 1 km (motile but not pelagic), or 10 km (highly mobile, pelagic). 
Variables were specified as 'multiple' for groups known to span more than 1 magnitude of range size. 
For groups to which sequences were annotated with high confidence, but for which life history strategy is diverse or poorly known (e.g. families in the phylum Nemertea), we used conservative, coarse approximations at a higher taxonomic rank. 
We assessed whether or not marine invertebrate taxa are thought to be present in Puget Sound by checking for their presence in a comprehensive checklist of invertebrates of Puget Sound CITE KOZLOFF. 
These data are available as part of the REFERENCE SUPPLEMENTAL DATA.

@@

\begin{figure}[h!] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{../../Figures/dissimilarity_from_shore.pdf}
    \caption{Pairwise dissimilarity (Bray-Curtis) across transects plotted against distance from shore. A linear model determined no effect of distance from shore on dissimilarity.}
  \label{dissimilarity_from_shore} % use this to refer to your figure in the text, so that numbering updates automatically
\end{figure}

\begin{figure}[h!] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{../../Figures/variance_from_shore.pdf}
    \caption{Within-OTU variance across transects plotted against distance from shore.}
  \label{variance_from_shore} % use this to refer to your figure in the text, so that numbering updates automatically
\end{figure}

\begin{figure}[h!] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{../../Figures/heatmap_sites.pdf}
    \caption{Heatmap of pairwise site dissimilarity (Bray-Curtis).}
  \label{heatmap} % use this to refer to your figure in the text, so that numbering updates automatically
\end{figure}
